SST_patterns

### 2020-01-19 SST_patterns.Rmd
update

# Reasons why upwelling might be detected at 10km rather than 50km
    # Dome in the isotherm blocking upwelling to reach the surface waters but does occur deeper down

>>>>

# Reasons why upwelling might be detected at 10km rather than 50km
    # Dome in the isotherm blocking upwelling to reach the surface waters but does occur deeper down
# (Figures folder - ig 2 and figure 10)
```
